NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-03-31 paper/discussion.tex
add open source comment add title to the appendix
integration grammar fix

\section{Discussion}
The current setup for the proposed tool is only suitable for natural language inference task. However, due to the modular design and the many shared attribution among end-two-end NLP models, we can readily extend the system to handle other tasks. We plan to add support for more NLP task, such as neural machine translation, question and answer, in the future.
%
From our evaluation process, we found that the quality of automatic perturbed sentences can be a potential limitation of the tool.
Since we rely on WordNet to generate the perturbation, which has a rather inclusive definition for synonymous. Often, we can identify perturbed sentences that are not particularly meaningful (e.g., sentences with very obscured words or usages). 
Even if all the words are meaning, currently, there is no way we can verify whether the perturbed sentence is valid natural language composition or not.
%
However, from natural language process point of view the perturbation of sentence while maintaining semantic and sentence correctness is an open research area on its own. 
%As better method appears, we can easily swap out the sentence perturbation functionality

To conclude, this work introduces a perturbation-driven visual interrogation system that provides the expert with a streamlined exploration environment for testing hypothesis and obtain intuition about the model. The proposed system frees the researchers from interruptions and tedious operations, therefore, allows them to focus on the more productive activities.

>>>>

\section{Discussion}
The current setup for the proposed tool is suitable only for natural language inference task. However, due to the modular design and the many shared attributions among the end-two-end NLP models, we can readily extend the system to handle other tasks. In the future, we plan to open source our projection and add support for more NLP tasks, such as neural machine translation and question-and-answer.
%
From our evaluation process, we found that the quality of automatic perturbed sentences can be a potential limitation of the tool, since we rely on WordNet to generate the perturbation, which has a rather inclusive definition for synonymous. Often, we can identify perturbed sentences that are not particularly meaningful (e.g., sentences with very obscure words or usages). 
Even if all the words are meaningful, currently, there is no way we can verify whether the perturbed sentence is valid natural language composition or not.
%
However, from the natural language process point of view, the perturbation of a sentence while maintaining semantic and grammar correctness is an open research area on its own. 
%As better method appears, we can easily swap out the sentence perturbation functionality

To conclude, this work introduces a perturbation-driven visual interrogation system that provides experts with a streamlined exploration environment for testing hypothesis and obtaining intuition about the model. The proposed system frees the researchers from interruptions and tedious operations, therefore, allows them to focus on more productive activities.

### 2018-03-31 paper/evaluation.tex
integration grammar fix

\section{Evaluation and Feedback}
The motivation for designing the proposed tool is driven by the error analysis challenges faced by our long-term collaborators working on natural language inference research. During the entire design and development process, we work closely with two NLP experts, and their constant evaluation and feedback have helped shape the tool we see today. 
%
Since these two NLP experts are heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.  To uncover the limitation and identify areas for improvements, we gathered a wider audiences from either visualization (4 researchers include 3 Ph.D. level student and one postdoc researcher) or NLP background (5 Ph.D. level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.

With the goal to identify the potential interface design issues, we first conduct an informal demonstration-and-feedback session with the visualization group. We start by explaining the basic natural language inference concept. We then demonstrate the features of the tool in detail while answering questions and address comments.
%
From this session, we have gathered complaints and suggestions on various aspect of the visual interface. Some of the identified issues include: (1) difficult to distinguish different type of predictions (distinct colors are added for the final version); (2) hard to recognize ground truth label (now, we use a green rectangle to indicate the ground truth); (3) lack of legends to understand the key elements in plots (legends are added). We address these interface issues before presenting the final version to the NLP group.

We conduct individual revaluation session with each participant from the NLP group, in which the participant is given 30 minutes to experiment with the tool after an overall feature demonstration. 
%
Since both the matrix and graph-based visual encoding is the most common attention representations used in NLP literature, most the participant can utilize them immediately and find the linked highlighting feature of the two views quiet useful.
% 
Once the participants familiarize with the tool, the first thing they try is often typing two similar sentences and examine the attention and prediction. After that, they will modified some words, or negate the hypothesis sentence, then check the attention and prediction again.
%
Such a ``perturb and observe'' operation demonstrates the most fundamental exploration strategy and matches well with the perturbation-driven paradigm the proposed tool aim to support.

One participant shows us two examples after a quick exploration session. 
In the first example, he identifies a case where the wrong attention alignment produces a correct final prediction.
%
In the other example, he finds a sentence pair with the incorrect attention that produces a wrong prediction. 
However, even after he forces the correct alignment, the prediction result remain incorrect. He believes observation such as these will provide valuable insights for him to interpret the model. 
%
Another participant comment that the ability to enable and disable update in the pipeline view is beneficial.

The participants also identify potential issues and places for improvement. 
One participant wishes the pipeline view could provide more detailed information compared to the current aggregated histogram visualization. 
Another participant suggests the possibility to examine multiple similar examples at a time (instead of one by one). 
%
Also, for the participants do not focus on NLI research, understand all the views at first can be a bit challenging. However, this issue can be addressed by the modular design, as the user can simply enable, only the sentence, attention, and prediction views, at first.
%
Overall, all the participants believe the proposed tool is very convenient for conduction experiment and exploring various hypothesis, which is essential to build intuitions about the model.

>>>>

\section{Evaluation and Feedback}
The motivation for designing the proposed tool is the error analysis challenges faced by our long-term collaborators working on natural language inference research. During the entire design and development process, we worked closely with two NLP experts, and their constant evaluation and feedback have helped shape the tool we see today. 
%
Since these two NLP experts have been heavily involved in the design process, they may not be the best candidates for identifying potential issues of the tool due to familiarity.  To uncover the limitation and identify areas for improvement, we gathered a wider audience from either visualization (4 researchers, including 3 Ph.D.-level students and one postdoc researcher) or NLP backgrounds (5 Ph.D.-level students who are familiar with the concept of natural language inference and attention) for obtaining feedback for the tool.

With the goal to identify the potential interface design issues, we first conducted an informal demonstration-and-feedback session with the visualization group. We started by explaining the basic natural language inference concept. We then demonstrated the features of the tool in detail. After that, we answered questions and seek feedback.
%
From this session, we have gathered complaints and suggestions on various aspects of the visual interface. Some of the identified issues include: (1) difficult to distinguish different types of predictions (distinct colors are added to the final version); (2) hard to recognize the ground truth label (we now use a green rectangle to indicate the ground truth); (3) lack of legends to understand the key elements in plots (legends are added). We address these interface issues before presenting the final version to the NLP group.

We conduct an individual revaluation session with each participant from the NLP group, in which the participant is given 30 minutes to experiment with the tool after an overall feature demonstration. 
%
Since both the matrix and graph-based visual encodings are the most common attention representations used in the NLP literature, most participants can utilize them immediately and find the linked highlighting feature of the two views quite useful.
% 
Once the participants familiarize with the tool, they often try to type two similar sentences and examine the attention and prediction. After that, they will modify some words, or negate the hypothesis sentence, and then check the attention and prediction again.
%
Such a ``perturb and observe'' operation demonstrates the most fundamental exploration strategy and matches well to the perturbation-driven paradigm the proposed tool aims to support.

One participant shows us two examples after a quick exploration session. 
In the first example, he identifies a case where the wrong attention alignment produces a correct final prediction.
%
In the other example, he finds a sentence pair with the incorrect attention that produces a wrong prediction. 
However, even after he forces the correct alignment, the prediction result remains incorrect. He believes observations such as these will provide valuable insights for him to interpret the model. 
%
Another participant comments that the ability to enable or disable model parameter update in the pipeline view is beneficial.

The participants also identify potential issues and places for improvement. 
One participant wishes the pipeline view could provide more detailed information compared to the current aggregated histogram visualization. 
Another participant suggests the possibility to examine multiple similar examples at a time (instead of one by one). 
%
Also, for the participants who do not focus on NLI research, understanding all the views at first can be a bit challenging. However, this issue can be addressed by the modular design, as the user can simply enable, only the sentence, attention, and prediction views.
%
Overall, all the participants believe the proposed tool is very convenient for conducting experiment and exploring various hypotheses, which is essential for building intuitions about the model.
